---
title: "LinkedIn"
author: "Razmig Zeitounian"
date: "7/23/2021"
output: html_document
---

Data Source: https://www.kaggle.com/killbot/linkedin-profiles-and-jobs-data 

```{r, message=FALSE}
library(tidyverse)
df <- read_csv("dump.csv") %>% 
  # drop ID column
  select(-X1)
```

```{r}
head(df)
```

```{r}
df %>% 
  sort(companyFollowerCount)
```

We start by checking how many observations we have and seeing how many of these individuals have at least 500 connections.

```{r}
dim(df)
at.least.500c <- df %>% 
  count(connectionsCount >= 500)
ggplot(as.data.frame(at.least.500c), aes(n)) + geom_bar()

ggplot(as.data.frame(at.least.500c), aes(`connectionsCount >= 500`, n, label = n)) + 
  geom_bar(stat = "identity", col = "blue", fill = "pink") +
  labs(x = "User has 500+ Connections", title = "Number of LinkedIn Users with 500+ Connections") +
  geom_text(hjust = 0.5, vjust = 10.5)
```

Another area we may be interested in is the age distribution of LinkedIn members.

```{r}
ggplot(df, aes(ageEstimate)) +
  geom_histogram(col = "cornsilk2", fill = "indianred", binwidth = 5) +
  labs(title = "Distribution of LinkedIn Users' Age")
```

We see that LinkedIn users tend to be on the younger side as the data are skewed right. This makes sense since LinkedIn is a networking platform and older people are less likely to be searching for jobs. We see practically no users of age 70 or greater.

```{r}

```

